Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-04 paperICSME.tex
añadiendo mas comentarios

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodr\'iguez-P\'erez\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jesus M. Gonzalez-Barahona\\
      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.urjc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{8 April 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\gema{Anadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}

@@

For these four projects we analyzed if bug fixes where introduce in their previous commits. For the first stage, we used the tool described in~\ref{sec:firstStage}. Each ticket was analyzed by two researchers independently. The second stage was done manually by the first author. %that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
\gema{He calculado la media, en minutos, del tiempo empleado en encontrar la causa del bug en cada ticket. La media a sido alrededor de 16 minutos.}
\gema{En el primer estudio realizado por Andrea y por mi con en análisis de 100 tickets, en la segunda fase obtuvimos un 74\% de similitud entre su analisis y el mio. Después de una revisión conjunta, incrementamos ese porcentaje hasta el 90 \% }

>>>>

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodr\'iguez-P\'erez\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jesus M. Gonzalez-Barahona\\
      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.urjc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{8 April 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\gema{Añadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}

@@

For these four projects we analyzed if bug fixes where introduce in their previous commits. For the first stage, we used the tool described in~\ref{sec:firstStage}. Each ticket was analyzed by two researchers independently. The second stage was done manually by the first author. %that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
\gema{He calculado el tiempo medio que cada investigador (Nelson, Dorealda y Yo) ha invertido en el análisis de los tickets ens la primera fase, usando la herrramienta. Siguiendo el orden: (3'6, 4, 3,6)}
\gema{He calculado la media, en minutos, del tiempo empleado en encontrar la causa del bug en cada ticket. La media a sido alrededor de 16 minutos.}
\gema{En el primer estudio realizado por Andrea y por mi con en análisis de 100 tickets; en la primera fase obtuvimos un porcentaje de acuerdo del 83\% incrementándolo hasta un 94\% tras una discusión entre ambas. En cuanto a la segunda fase, obtuvimos un 74\% de similitud entre su análisis y el mio. Después de una revisión conjunta, incrementamos ese porcentaje hasta el 90\%. En este estudio la clasificaión de la segunda fase salió (53\% ,35\% y 11\%) pero no habíamos quitado los falsos positivos.}
